---
title: "Assessmnet-1 Part-1"
author: "Ryosuke Otsuka s4663911"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Setup your Assessment 1 project:

2 Create the heading of the first level and call it RMarkdown editing 

# RMarkdown editing

3. Write 2-3 sentences about RMarkdown (you can google this information or use resources recommended in class - no need to reference)

4. In the above use bold and italics for editing.

**R Markdown** provides an *unified authoring framework for the data science, integrating your code, its results.* R Markdown doccuments are fully repeatable and support multiple formats, **such as PDFs**, **Word files.** 

5. Review the suggested documentation on how to insert links in the .rmd file and include an in-text link to https://rmarkdown.rstudio.com/lesson-8.html 

[here](https://rmarkdown.rstudio.com/lesson-8.html)

6. Insert an R chunk and create a variable with this dataset

```{r}
fastfood <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

7. Display the first 10 rows of the dataset using head() and kable(). Display the first 10 rows of the dataset and the first 5 variables

```{r}
library(tidyverse)

library(knitr)

head(fastfood, 10)
```

```{r}
kable(head(fastfood[, 1:5]), "pipe")
```






