---
title: "Assessmnet-1 Part-1"
author: "Ryosuke Otsuka s4663911"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Setup your Assessment 1 project:

2 Create the heading of the first level and call it RMarkdown editing 

# RMarkdown editing

3. Write 2-3 sentences about RMarkdown (you can google this information or use resources recommended in class - no need to reference)

4. In the above use bold and italics for editing.

**R Markdown** provides an *unified authoring framework for the data science, integrating your code, its results.* R Markdown doccuments are fully repeatable and support multiple formats, **such as PDFs**, **Word files.** 

5. Review the suggested documentation on how to insert links in the .rmd file and include an in-text link to https://rmarkdown.rstudio.com/lesson-8.html 

[here](https://rmarkdown.rstudio.com/lesson-8.html)

6. Insert an R chunk and create a variable with this dataset

```{r}
fastfood <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

7. Display the first 10 rows of the dataset using head() and kable(). Display the first 10 rows of the dataset and the first 5 variables

```{r}
library(tidyverse)

library(knitr)

head(fastfood, 10)
```

```{r}
kable(head(fastfood[, 1:5]), "pipe")
```


## Part_2

8. Display the observations that has more than 1000 calories

```{r}
fastfood %>%
  filter(calories > 1000) %>%
  head(n = 30)
```

9. Arrange observations with more than 40 in total_fat and more than 80 in total_carb in the descending order (PLEASE USE THE VARIABLE OF YOUR CHOICE TO ORGANISE THE DESCENDING ORDER) and save them to a new variable (dataset) called `dont_eat_this`

```{r}
dont_eat_this <- fastfood %>%
  filter(total_fat > 40, total_carb > 80) %>%
  arrange(total_fat, total_carb = TRUE)
```

10. Using the initial dataset variable, use `case_when()` to create a new variable `heavy_food` which is equal to "heavy" when total calories are greater than 500, "low" when total calories are less than 250 and "average" for all other cases. Count the number of observations in each created category.


```{r}
fastfood <- fastfood %>%
  mutate(heavy_food = case_when(calories > 500 ~ "heavy", 
                                calories < 250 ~ "low", 
                                TRUE ~ "avarage"))

fastfood %>%
count(heavy_food, sort = TRUE, name = "Calories category")
```


11. Display the types of variables in the dataset using `skimr` package 

```{r}
library(skimr)

skim(fastfood)
```

12. Present the count observations from each restaurant in a descending order

```{r}
fastfood %>%
  count(restaurant, sort = TRUE)
```

13. Using groupings (group_by()), summarise and display the average number of calories for each restaurant.

```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(mean(calories)) %>%
  ungroup() %>%
  kable()
```


14. Add variables to the dataset, which:

-  calculates the average calories per type of restaurant and call it `average_calories` 
-  calculates the maximum total_fat per type of restaurant and call it `max_fat` 
-  calculates the minimum cholesterol per type of restaurant and call it `min_cholesterol` 


```{r}
fastfood <-fastfood %>%
  group_by(restaurant) %>%
  mutate("avarege_calories" = mean(calories)) %>%
  ungroup() %>%
  kable()
```

```{r} 
fastfood <- fastfood %>%
  group_by(restaurant) %>%
  mutate("max_fat" = max(total_fat)) %>%
  ungroup()
  
```

```{r}
fastfood <- fastfood %>%
  group_by(restaurant) %>%
  mutate("min_cholesterol" = min(cholesterol)) %>%
  ungroup()
  
```


15. Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best. 

```{r}
fastfood %>%
  ggplot(aes(restaurant, total_fat, fill = restaurant)) +
  geom_col() +
  coord_flip() +
  labs(x = "Type of Restaurant", y = "Total Fat", fill = 
         "restaurant",title = "Total fat of each restaurants")
```
Type of restaurant is categorised as a discrete valuable, whereas total fat is a continuous valuable. In this case, geom_col is the most suitable data visualisation in order compare the total fat with each type of restaurant.  


16. Add a variable to the dataset, which calculates the sum of cholesterol and sodium and call it `cholesterol_sodium`.
Remove the variable `salad`

```{r}

fastfood <- fastfood %>%
  mutate(cholesterol_sodium = cholesterol + sodium, "salad" = NULL)


```


17. Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` 

```{r}
fastfood %>%
  filter(restaurant == "Mcdonalds") %>%
  ggplot(aes(sugar, protein, col = "restaurant")) + geom_point() 
 
```

18. Identify variable(s) which should be factors and transform their type into a factor variable.

```{r}
fastfood <- fastfood %>% mutate_if(is.character, factor)

```

There are three charactor valuable ("restaurant", "item", "heavy_food") which should be changed to factor.   



```{r}
skim(fastfood)
```


19. Create two new variables:
Read about `cut_number()` function using Help and add a new variable to the dataset `calories_type`. Use `calories` variable for `cut_number()` function to split it into 3 categories `n=3`, add labels `labels=c("low", "med", "high")` and make the dataset ordered by arranging it according to calories. 

```{r}
fastfood %>%
  mutate(calories_type = cut_number(calories, n = 3, labels=c("low", "med", "high"))) %>%
  arrange(desc(calories))
```

20. Create a dataviz that shows the distribution of `calories_type` in food items for each type of restaurant. Think carefully about the choice of data viz. Use facets, coordinates and theme layers to make your data viz visually appealing and meaningful. Use factors related data viz functions.

```{r}
library(ggplot2)

calories_types <- fastfood %>%
  mutate(calories_type = cut_number(calories, n = 3,labels=c("low", "med", "high")))

calories_types %>%
  ggplot(aes(restaurant, calories_type, col = restaurant)) +
  geom_jitter() + 
  coord_flip()
```


21. The second variable should show the percentage of `trans_fat` in `total_fat`. Add the variable to the dataset and call it `trans_fat_percent`. Do not forget to save the updated dataset. 

```{r}
fastfood <- fastfood %>%
  mutate(trans_fat_persent = trans_fat / total_fat * 100)
```

22. Create a dataviz that shows the distribution of `trans_fat` in food items for each type of restaurant. Think carefully about the choice of data viz. Use facets, coordinates and theme layers to make your data viz visually appealing and meaningful.

```{r}
fastfood %>%
  ggplot(aes(restaurant, trans_fat, fill = restaurant)) + 
  geom_col() + 
  facet_wrap(~ trans_fat) +
  coord_flip() + 
  labs(x = "Types of restaurants", y = "Trans_fat") +
  theme_get()
  
```


23. Calculate and show the average (mean)  `total_fat` for each type of restaurant. No need to save it as a variable.

```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(mean(total_fat))

```


24. And create a dataviz that allow to compare different restaurants on this variable (`total_fat`). You can present it on one dataviz (= no facets). 
Think carefully about the choice of data viz. Use coordinates and theme layers to make your data viz visually appealing and meaningful. 


```{r}
fastfood %>%
  group_by(restaurant) %>%
  mutate("average_fat" = mean(total_fat)) -> average_fat 

average_fat %>% 
  ggplot(aes(restaurant, total_fat, fill = restaurant)) + 
  geom_boxplot() + 
  coord_flip()
  
  
```





