---
title: "Assessmnet-1 Part-1"
author: "Ryosuke Otsuka s4663911"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Setup your Assessment 1 project:

2 Create the heading of the first level and call it RMarkdown editing 

# RMarkdown editing

3. Write 2-3 sentences about RMarkdown (you can google this information or use resources recommended in class - no need to reference)

4. In the above use bold and italics for editing.

**R Markdown** provides an *unified authoring framework for the data science, integrating your code, its results.* R Markdown doccuments are fully repeatable and support multiple formats, **such as PDFs**, **Word files.** 

5. Review the suggested documentation on how to insert links in the .rmd file and include an in-text link to https://rmarkdown.rstudio.com/lesson-8.html 

[here](https://rmarkdown.rstudio.com/lesson-8.html)

6. Insert an R chunk and create a variable with this dataset

```{r}
fastfood <- read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

7. Display the first 10 rows of the dataset using head() and kable(). Display the first 10 rows of the dataset and the first 5 variables

```{r}
library(tidyverse)

library(knitr)

head(fastfood, 10)
```

```{r}
kable(head(fastfood[, 1:5]), "pipe")
```


## Part_2

8. Display the observations that has more than 1000 calories

```{r}
fastfood %>%
  filter(calories > 1000)
```

9. Arrange observations with more than 40 in total_fat and more than 80 in total_carb in the descending order (PLEASE USE THE VARIABLE OF YOUR CHOICE TO ORGANISE THE DESCENDING ORDER) and save them to a new variable (dataset) called `dont_eat_this`

```{r}
dont_eat_this <- fastfood %>%
  filter(total_fat > 40, total_carb > 80) %>%
  arrange(total_fat, total_carb = TRUE)
```

10. Using the initial dataset variable, use `case_when()` to create a new variable `heavy_food` which is equal to "heavy" when total calories are greater than 500, "low" when total calories are less than 250 and "average" for all other cases. Count the number of observations in each created category.


```{r}
fastfood <- fastfood %>%
  mutate(heavy_food = case_when(calories > 500 ~ "heavy", 
                                calories < 250 ~ "low", 
                                TRUE ~ "avarage"))

fastfood %>%
count(heavy_food, sort = TRUE, name = "Calories category")
```


11. Display the types of variables in the dataset using `skimr` package 

```{r}
library(skimr)

skim(fastfood)
```

12. Present the count observations from each restaurant in a descending order

```{r}
fastfood %>%
  count(restaurant, sort = TRUE)
```

13. Using groupings (group_by()), summarise and display the average number of calories for each restaurant.

```{r}
fastfood %>%
  group_by(restaurant) %>%
  summarise(mean(calories)) %>%
  ungroup() %>%
  kable()
```


14. Add variables to the dataset, which:

-  calculates the average calories per type of restaurant and call it `average_calories` 
-  calculates the maximum total_fat per type of restaurant and call it `max_fat` 
-  calculates the minimum cholesterol per type of restaurant and call it `min_cholesterol` 


```{r}
fastfood %>%
  group_by(restaurant) %>%
  mutate("avarege_calories" = mean(calories)) %>%
  ungroup() %>%
  kable()
```

```{r}
fastfood %>%
  group_by(restaurant) %>%
  mutate("max_fat" = max(total_fat)) %>%
  ungroup() %>%
  kable()
```

```{r}
fastfood %>%
  group_by(restaurant) %>%
  mutate("min_cholesterol" = min(cholesterol)) %>%
  ungroup() %>%
  kable()
```


15. Display the data vis of total fat per each type of restaurant. Write a narration (2-3 sentences) why you believe this type of data viz presents such information best. 



16. Add a variable to the dataset, which calculates the sum of cholesterol and sodium and call it `cholesterol_sodium`.


```{r}

```

Remove the variable `salad`

```{r}
fastfood %>%
  rm("salad")
```


17. Use observations for Mcdonalds to plot sugar variable against protein with `geom_point()` 



